Hydras \& Co.

### 2022-03-10 doc/part-hydras.tex
more gaia-compatible names
small changes (book)

\subsection*{Compatibility with \gaia\cite{Gaia} (in progress)}
The \gaia project~\cite{Gaia} by Jos\'e Grimm aimed to formalize mathematics in \coq  in
the style of Nicolas Bourbaki. It contains many definitions and results about ordinal numbers. In Chapter~\ref{gaia-chapter}, we present some modules which allow \HydrasLib' users to apply lemmas proven in \gaia, and vice versa.

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}

  In \texttt{gaia.ssete9}, the $n$-th finite ordinal is written
  \texttt{$\backslash${F}\,$n$}. There is no coercion in \gaia from \texttt{nat} to finite ordinals.

@@

\paragraph{\gaiacompat (cf. Remark ~\vref{remark:hydra-gaia-renaming})}
In \texttt{gaia.ssete9}, the ordinal $\omega$ is bound to
a \emph{constant} called \texttt{T1omega}.

@@

\paragraph{\gaiacompat (cf. Remark ~\vref{remark:hydra-gaia-renaming})}
In \texttt{gaia.ssete9} the identifier\texttt{phi0} is bound to a constant (not a notation).

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In ~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge},
we define a variant of \texttt{pp} for pretty-printing terms of type \texttt{ssete9.CantorOrdinal.T1} (see Sect.~\vref{sect:gaia-ppT1}).

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the strict order \texttt{T1lt} on ordinal terms is directly defined as a boolean function (in \ssreflect's style).

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the boolean function which characterizes ordinal terms in normal form is defined as follows:

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, the boolean functions associated with limit and successor ordinals are called \texttt{T1limit} and \texttt{T1is\_succ}.

@@

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
We keep \gaia's base names for
addition and multiplication of ordinal terms below $\epsilon_0$.
Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.

>>>>

\subsection*{Compatibility with \gaia\cite{Gaia} (in progress)}
The \gaia project~\cite{Gaia} by Jos\'e Grimm aimed to formalize mathematics in \coq  in
the style of Nicolas Bourbaki. It contains many definitions and results about ordinal numbers. In Chapter~\ref{gaia-chapter}, we present some modules which allow \HydrasLib' users to apply lemmas proven in \gaia, and vice versa. Remarks about compatibility with \gaia signalled with the picture \gaiasign.

@@

\paragraph*{\gaiasign}
  In \texttt{gaia.ssete9}, the $n$-th finite ordinal is written
  \texttt{$\backslash${F}\,$n$}. There is no coercion in \gaia from \texttt{nat} to finite ordinals.

@@

\paragraph*{\gaiasign}
In \texttt{gaia.ssete9}, the ordinal $\omega$ is also named as \emph{constant}  \texttt{T1omega}.

@@

\paragraph*{\gaiasign}
In \texttt{gaia.ssete9} the identifier\texttt{phi0} is bound to a constant (not a notation).

@@

\paragraph*{\gaiasign}
In ~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge},
we define a variant of \texttt{pp} for pretty-printing terms of type \texttt{ssete9.CantorOrdinal.T1} (see Sect.~\vref{sect:gaia-ppT1}).

@@

\paragraph*{\gaiasign}
In \gaia, the strict order \texttt{T1lt} on ordinal terms is directly defined as a boolean function (in \ssreflect's style).

@@

\paragraph*{\gaiasign}
In \gaia, the boolean function which characterizes ordinal terms in normal form is defined as follows:

@@

\paragraph*{\gaiasign}
In \gaia, the boolean functions associated with limit and successor ordinals are called \texttt{T1limit} and \texttt{T1is\_succ}.

@@

\paragraph*{\gaiasign}
We keep \gaia's base names for
addition and multiplication of ordinal terms below $\epsilon_0$.
Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.
